\cvsection{Experience}
\begin{cventries}
  \cventry
    {SOFTWARE ENGINEER INTERNSHIP}
    {Foodvisor, SA}
    {Paris, France}
    {Jun. 2016 - Sept. 2016}
    {
      \begin{cvitems}
        \item {Full-stack development of an Android mobile application}
        \item {Smooth gestures/animations, local storage, complete onboarding, camera manipulation, API calls, multilingual, SVG manipulation, unit tests}
        \item {Stack: React-Native/Redux }
        \item {Test-ready}
      \end{cvitems}
    }
  \cventry
    {R\&D INTERNSHIP}
    {Microsoft France}
    {Issy-les-Moulineaux, France}
    {Jun. 2012 - Sept. 2012}
    {
      \begin{cvitems}
        \item {Implemented a software that analyzes the user requests on Bing search engine - currently used by engineers at Microsoft}
        \item {Visual Studio, SVN, C#, ASP.NET, and other Microsoft tools. English-spoking environment}
        \item {Award of the youngest intern at Microsoft (18 yo)}
      \end{cvitems}
    }
  \cventry
    {DEVELOPPER}
    {LIRMM}
    {Montpellier, France}
    {Apr. 2015 - Jun. 2016}
    {
      \begin{cvitems}
        \item {Full-stack creation of ATGC: Benchmark tool}
        \item {Design of a clustered architecture}
        \item {Stack: NodeJS/ReactJS/Redis/MongoDB (Javascript)}
        \item {Production-ready. (http://github.com/mehdichamouma/atgc)}
      \end{cvitems}
    }
  \cventry
    {Regional Referee, private teacher and software developper}
    {FFBB, Acadomia and TheRunship}
    {Montpellier, France}
    {Sept. 2015 - June. 2017}
    {}
\end{cventries}
